\documentclass[]{article}

%opening
\title{Project Assignment A - Outline}
\author{Søren Winkel Holm s183911 \\ Oskar Eiler Wiese Christensen s183917 \\ Anders Henriksen s183904}

\begin{document}
	
	\maketitle
	
	\section*{Outline}
	\begin{itemize}
		\item "funny" introduction
		
		Welcome to the world of game of thrones; where the characters are plentiful and complicated, and the shock value is more for show than for actual character development. If season 8 has taught us anything, it is that for the show to be any good, we have to write it ourselves. To do so, it would help to have a good understanding of how the most important characters in the books interact with and relate to each other. Meanwhile, it is also important to satisfy the neckbeard stans on reddit. In other words, we want to find the relations between characters in the hivemind of reddit and in the actual books.
		
		\item Size and origins of social graphs
		
		This will be possible using two social graphs; one constructed using the text from the ebooks and one constructed using posts on the r/asoiaf subreddit. For the ebook social graph, every character is a node and a link is created if two characters are mentioned in the same chapter. This leads to a network with \textbf{NODES} nodes and \textbf{LINKS} links and a dataframe of \textbf{ROWS} rows and \textbf{VARIABLES} variables. For the reddit data, we extracted every submission title and text between \textbf{DATE1} and \textbf{DATE2}. We removed all submissions without text and where no characters are mentioned. Afterwards, we connected the character nodes with links if they are mentioned in the same submission. This left us with a network with \textbf{NODES} nodes and \textbf{LINKS} links and a dataframe have \textbf{ROWS} rows and \textbf{VARIABLES} variables. In total, this leaves us with a total of \textbf{MB} MB of data and a total of \textbf{NODES} nodes and \textbf{LINKS} links. Meanwhile, the final pandas dataframe have \textbf{ROWS} rows and \textbf{VARIABLES} variables in total.
		
		\item What do we do from here?
		
		With these two social graphs, we see a substantial difference between how Reddit views the character relations vs how the characters actually relate. This means that for project B, 
		
		
		
	\end{itemize}

\end{document}
